---
title: " Is batman somewhere ?"
author: "Augusta Mukam, Fred Dagang"
date: "December, 2021"
output:
  pdf_document: default
  html_document:
    df_print: paged
---



First we get the data.
```{r}
data_path = "bats.csv"
mydata = read.table(file = data_path, sep=";", skip=3, header= T)
mydata
```

# 1. Study of the relationship between brain weight and body mass

Because, BRW and BOW variable s don't have the same order of magnitude, we divide the column of BRW by 1000.

```{r}
mydata$BRW <- mydata$BRW/1000
phyto = mydata[(mydata$Diet == 1),]
plot(phyto)
```
 
 Then We can plot a figure showing the dependence of body mass and brain weight.
```{r}
library(ggplot2)
ggplot(mydata, aes(x=BOW,y=BRW)) + 
  geom_point() +
  #geom_line() + 
  ggtitle("Brain weight and body mass") +
  xlab("Body mass ") + 
  ylab("Brain weight")
```

Then we obtain the mathematical form of the model based on a **simple regression model**.
```{r}
reg1 = lm(BRW~BOW, data = phyto)
summary(reg1)
```

The estimate of the intercept is **0.6234**. The coefficient of determination is **alpha1 = 0.0089**.
**BRW = alpha1 * BOW + intercept**

The **H0 hypothesis is : alpha1 = intercept = 0**. So we reject it.
Brain weight depends strongly on body mass.


Now we analyse the variance.
```{r}
anova(reg1)
```

We can see the MSM, MSE, Degree of freedom.
The sum of residual squares is **MSE = 4.254**

Now we plot the graph of the residuals.
```{r}
plot(reg1$fitted.values, reg1$residuals, xlab = "Predicted", ylab = "Residuals")
```

It appears to this graph one very distant point.

```{r}
plot(reg1,4)
which(phyto$BRW>8)
```

So we have one individual point. We redo the analysis by removing this point.
```{r}
phytobis = phyto[which(phyto$BRW < 8),]
reg2 = lm(BRW ~ BOW, data = phytobis)
summary(reg2)
```

```{r}
par(mfcol = c(2,2))
plot(reg1)
plot(reg2)
```

Discussion : 

# 2. Study of the contribution to the total weight od each part of the brain

```{r}
library(corrplot)
```

```{r}
phytoNum = phyto[, c(4:8)]
mat.cor = cor(phytoNum)
corrplot(mat.cor, type = "upper")
```
```{r}
cor.test(phyto$BRW, phyto$HIP)
```

BRW variable depend on HIP variable.

```{r}
cor.test(phyto$BRW, phyto$MOB)
```

BRW variable depend on MOB variable.
```{r}
cor.test(phyto$BRW, phyto$AUD)
```

BRW variable doesn't depend enough on AUD variable.

Now we run some multiple regression model.
```{r}
regm = lm(BRW~AUD+MOB+HIP, data = phytobis)
summary(regm)
```

The estimate of the intercept is **-0.3126**. The coefficients of determination are **alpha1 = 0.048**, **alpha2 = -0.0024** and **alpha3 = 0.016**.

**BRW = alpha1 * AUD + alpha2 * MOB + alpha3 * HIP + intercept**

The **H0 hypothesis is : alpha1 = alpha2 = alpha3 = intercept = 0**. So we reject it.
Brain weight (BRW) depends strongly on the volume of the auditory part of the brain (AUD) and the hippocampus (HIP). But it doesn't depend a lot on the volume of the olfactory zone (MOB). So we can remove the variable MOB in the model.


Now we analyse the variance.
```{r}
anova(regm)
```


```{r}
reg0 = lm(BRW ~ 1, data = phyto)
step(reg0, scope=BRW~AUD + MOB + HIP, discretion = "forward")

```

The purpose of this test is 


# 3. Link between volume of the auditory part and diet.

```{r}
mydata$Diet_F = as.factor(mydata$Diet)
with(mydata, plot(AUD~Diet))
with(mydata, plot(AUD~Diet_F))
```

Now we do the regression analysis.
```{r}
lm = lm(AUD~Diet_F, data = mydata)
anova(lm)
```

So we can conclude that auditory brain volume (AUD) and diet (Diet) are not really linked.