---
output:
  pdf_document: default
  html_document: default
---
# Is batman somewhere

First we get the data
```{r}
data_path = "bats.csv"
mydata = read.table(file = data_path, sep=";", skip=3, header= T)
mydata
```

```{r}
phyto = mydata[(mydata$Diet == 1),]
mydata$BRW <- mydata$BRW/1000
```
 Then We can plot a figure showing the dependance of body mass and brain weight
 Bow(g) B
```{r}
library(ggplot2)
ggplot(mydata, aes(x=BOW,y=BRW)) + 
  geom_point() +
  #geom_line() + 
  ggtitle("brain weight and body mass") +
  xlab("Body mass ") + 
  ylab("Brain weight")
```
Then we obtain the mathematical form of the model
```{r}
reg1 = lm(BRW~BOW, data = phyto)
summary(reg1)
```
The estimate of the intercept is **623.4469**. The coefficient of determination is **8.9999**.
BRW = alpha * BOW + intercept
The H0 hypothesis is : alpha1 = intercept =0. So we reject it.
Brain weight depends strongly on body mass


Now we analyse the variance
```{r}
anova(reg1)
```
We can see the MSM, MSE, Degree of freedom.
**MSE = 4253838**


```{r}
plot(reg1$fitted.values, reg1$residuals, xlab = "Predicted", ylab = "Residuals")
```
It appears to this graph some points wich large difference of value

```{r}
#phyto=phyto[phyto$BRW < 8,]
which(phyto$BRW>8)
```


```{r}
plot(reg1,4)
phytobis = phyto[which(phyto$BRW < 8),]
reg2 = lm(BRW~BOW,data=phytobis)
summary(reg2)
```
```{r}
par(mfcol = c(2,2))
plot(reg1)
plot(reg2)
```



```{r}
library(corrplot)
```

```{r}
phytoNum = phyto[, c(4:8)]
mat.cor = cor(phytoNum)
corrplot(mat.cor, type = "upper")
```
```


```{r}
cor
```

```{r}
summary(simple_reg)
```
```{r}
acf(residuals(simple_reg))
```


```{r}
ggplot(mydata, aes(x=circ, y=height)) + geom_point() + stat_smooth(method = "lm", se=FALSE) + xlab("circ") + ylab("height")
```


```{r}
i=4
plot(simple_reg,i)
#plot(simple_reg$residuals)
```
```{r}
predict(simple_reg, data.frame(circ=10), interval="prediction")
```
# Multivariate regression

```{r}
mydata$circ_sqrt <- sqrt(mydata$X70)
```

```{r}
multi_reg <- lm(height~circ+circ_sqrt,data=mydata)
summary(multi_reg)
```
```{r}
multi_reg_2 <- lm(height~circ_sqrt, data=mydata)
summary(multi_reg_2)
```


```{r}
circ_pred <- seq(0.175,len=1000)
height_pred <- multi_reg_2$coefficients[1] + multi_reg_2$coefficients[2]*sqrt(circ_pred)
fct_reg <- data.frame(circ_pred=circ_pred, height_pred=height_pred)
ggplot()+
  geom_point(data = mydata, aes(x = circ, y= height))+
  geom_line(data=fct_reg, aes(x=circ_pred, y=height_pred), col="blue")+
  stat_smooth(method = "lim", se=FALSE)+
  xlab("circ")+
  ylab("height")
```
```{r}
plot(multi_reg_2)
```





