---
title: "03_Names-Methodo2022-exercise"
author: "Augusta Mukam"
date: "October, 2021"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

# Description of the work

The aim of the activity is to develop a methodology to answer a specific question on a given dataset. 

## Environment packages

```{r}
# The environment
library(tidyverse)
library(ggplot2)
library(readr)
library(dplyr)
```

# Description of the dataset

The dataset is the set of Firstname given in France on a large period of time. 


We download Raw Data from the website
```{r}
file = "dpt2020_txt.zip"
if(!file.exists(file)){
  download.file("https://www.insee.fr/fr/statistiques/fichier/2540004/dpt2020_csv.zip",
	destfile=file)
}
```
We unzip the file _dpt2020_csv.zip_ file to get the **dpt2020.csv** file. 
```{r}
unzip(file)
```

## Build the Dataframe from file
```{r}
FirstNames <- read_delim("dpt2020.csv",delim =";")
```
## Description of the dataset

To retrieve the full column specification for this data, we use spec()

```{r}

```
```{r}
FirstNames
```


# Scientific report.

1. **Choose a firstname and analyse its frequency along time. Compare several firstnames frequency**

First, we count the different firstnames of the dataset by decreasing order

```{r}
count = table(FirstNames$preusuel)
sort(count,  decreasing = TRUE)
```
We see that **Camille** is the mos frequent firstName, so we decide to study its frequency per year.

il faut absolument respecter la case sur les noms
```
frequencies=FirstNames %>% group_by(annais) %>%count(preusuel) %>% arrange(desc(frequency))

```


```{r}
frequencies=FirstNames%>% group_by(annais) %>% filter(preusuel=="CAMILLE") %>% summarise(n = n()) %>% arrange(desc(n))
frequencies
```

```{r}

```


2. **Establish, by gender, the most given firstname by year** 
```{r}

```
3. Make a short synthesis

```{r}

```
4. Advanced (not mandatory) : is the firstname correlated with the localization (department) ? What could be a method to analyze such a correlation.

```{r}

```
The report should be a pdf knitted from a  notebook (around  3 pages including figures), the notebook and the report should be delivered.
